Paper: Convex Covering

### 2023-12-28 els2024-convex-covering/paper.tex
Two more citations

>>>>

Wei et al.\cite{wei2022coacd} present a much improved method for approximate convex decomposition that is especially tuned for collision handling. However, their approach is extremely complex and difficult to implement, relying on many other algorithm implementations, such as 2D triangulation and monte-carlo tree search, which we would have had to reproduce in Lisp. Liu et al.'s original work only requires on an implementation of the Quickhull\cite{barber1996quickhull} algorithm.
